---
title: "CV of Ted Laderas, PhD"
author: Ted Laderas
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1co40b1-0elS86Ttk77Kf8cEBGGjjiSaNLohtgZ5eRH4/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _laderast.github.io/cv_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://laderast.github.io/cv/cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.



Main
================================================================================

Ted Laderas, PhD {#title}
--------------------------------------------------------------------------------

**Bioinformatics Trainer**, DNAnexus

I am passionate about teaching students to think about data, and have taught Data Science to a variety of groups, including graduate students, post-docs, staff, and clinicians. I am also an RStudio Certified Trainer in both the `tidyverse` and `Shiny`.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Teaching {data-icon=chalkboard-teacher data-concise=true}
--------------------------------------------------------------------------------

### Teaching Statement

N/A

N/A

N/A

I believe in democratizing data science. To this end, I have been involved with several national educational efforts: Big Data to Knowledge, National Library of Medicine's efforts with data science. My workshops, lectures and lessons have been utilized at multiple schools, and by multiple audiences, including clinicians, bioinformaticians, undergraduates. 

I utilize evidence-based pedagogical techniques in my teaching, specifically active learning and psychological safety. I am a firm believer in making students feel psychologically safe and giving them space to be curious. Many of my students have become collaborators in my teaching materials, improving them with their ideas and their questions. As a result, my work has been recognized as being accessible to a wide audience.

I believe that we must give graduate students more transferrable skills, and so I have co-founded BioData Club, a community of practice at OHSU and beyond that focuses on teaching and learning data science skills. I am dedicated to my students, and courses and workshops show consistently high ratings and evaluations. I am also a certified instructor for both The Carpentries and RStudio. 

In my educational work, I have focused on *Exploratory Data Analysis* (EDA) as a way to be curious and to not be afraid of your data, *Predictive Modeling and Data Analytics*, *interactive visualization*,*Open Science*, *Team Science*, and the importance of *interdisciplinary collaboration*. I am dedicated to making my work accessible and reproducible by others.




Courses {data-icon=chalkboard-teacher data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("course")
```

Educational Scholarship {data-icon=chalkboard-teacher data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("educational_scholarship")
```

Research {data-icon=flask data-concise=true}
--------------------------------------------------------------------------------

### Research Statement

N/A

N/A

N/A

My research interests are complex diseases, precision medicine, applications of systems science (including network analysis and modeling), and applying data integration to difficult and high-impact translational research questions. These questions include immune system profiling in both infectious disease (tuberculosis) and Acute Myeloid Leukemia, understanding drug sensitivity in the context of multiple cancer types (AML, Colorectal, Breast and Head and Neck Cancer), and quantifying expression differences in alcoholic preference. I have worked with a large number of datatypes (high-throughput immunophenotyping, proteomics, expression, genomic, and functional drug screen data) and have focused on methods and frameworks integrating these datatypes within the biological and clinical context of these translational research questions. 

My training in biomedical informatics as a master’s student in Biomedical Informatics, as an NLM Predoctoral Fellow, and as a NLM Postdoctoral fellow has enabled me to communicate with a wide variety of collaborators by giving me a strong background in Cancer Biology, Software Development, and Clinical Systems. 

Additionally, I am a strong advocate for Open Science initiatives, most notably the effort for reproducibility in scientific analysis. To this end, I have developed multiple novel software pipelines that transparently process data from raw data to through the final stages of analysis.

Research Software/Intellectual Property {data-icon=laptop data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("software")
```


Selected Publications, Posters, and Talks {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```


Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('data_science_writing_aside')
```
:::

```{r}
CV %<>% print_section('data_science_writings')
```


Service {data-icon=info-circle}
--------------------------------------------------------------------------------

### Service Statement

N/A

N/A

N/A

I am a strong supporter of service at OHSU and beyond. I currently participate in the DMICE BCB (Bioinformatics and Computational Biology) Faculty Division meeting, the DMICE Mentoring committee, and have participated in the BCB Curriculum Retreat in order to plan upcoming coursework at DMICE. As a Pacific Islander, I have a unique viewpoint about diversity and have dedicated myself to making classes and workshops psychologically safe. 

Beyond OHSU, I believe that we need to increase public engagement of science and increase outreach and mentoring of next-generation science students, especially from disadvantaged populations will enable these students to succeed in STEM-based careers. 

As a former student of Saturday Academy’s scientific mentoring program, I want to contribute back to this community and engage potential STEM students through student outreach and mentoring. I am also involved in outreach through the development of course material for the Biocatalyst training program through Oregon Bioscience Association, which provides bioscience training for unemployed or under-employed professionals.

Service History and Accomplishments
----------------------------------------------------------------------------------------

```{r}
CV %<>% print_section('service')
```


Positions and Work Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('positions')
```

Completed Support
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('funding_current')
```

```{r}
CV %<>% print_section('funding_complete')
```

```{r}
CV %<>% print_links()
```
