---
title: "Ted Laderas's CV"
author: Ted Laderas
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1co40b1-0elS86Ttk77Kf8cEBGGjjiSaNLohtgZ5eRH4/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _laderast.github.io/cv_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/laderast/cv/raw/master/laderas_cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available [on github.com/laderast/cv](https://github.com/laderast/cv).

Last updated on `r Sys.Date()`.



Main
================================================================================

Ted Laderas, PhD {#title}
--------------------------------------------------------------------------------

**Assistant Professor**, Division of Bioinformatics and Computational Biology, Department of Medical Informatics and Clinical Epidemiology

**Researcher**, OHSU Knight Cancer Institute

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



Software {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("software")
```


Courses {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('teaching_experience_aside')
```
:::

```{r}
CV %<>% print_section("course")
```


Educational Resources {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("educational_resource")
```



Selected Publications, Posters, and Talks {data-icon=book}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('research_experience_aside')
```
:::

```{r}
CV %<>% print_section('academic_articles')
```


Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('data_science_writing_aside')
```
:::

```{r}
CV %<>% print_section('data_science_writings')
```



Selected Press (About)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
#CV %<>% print_section('about_me_press')
```


<br>
<br>


Selected Press (By)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
#CV %<>% print_section('by_me_press')
```




Positions and Work Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('positions')
```


```{r}
CV %<>% print_links()
```

